Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-13 sections/climate.tex
Improved WorldClim data description

WorldClim \citep{data:worldclim} is a high resolution climate dataset interpolated between from weather station data over global land areas. The interpolation uses 30\,arc\,s aggregated, hole-filled SRTM\needref data \todo{check WorldClim methods}, which provides a resolution much higher than attained by general circulation models.

>>>>

WorldClim \citep{data:worldclim} is a high resolution climate dataset built from observation data. These climate surfaces were generated by spatial interpolation between a large set of weather stations using a 30\,arc\,s-aggregated flavour of hole-filled SRTM data over global land areas. This provides a resolution much higher than attained by general circulation models.
